\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}


\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{stmaryrd}

\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Primes}{\mathbb{P}}
\newcommand{\st}{\text{ s.t. }}
\newcommand{\txtand}{\text{ and }}
\newcommand{\txtor}{\text{ or }}
\newcommand{\lxor}{\veebar}

\begin{document}
	
	\author{Paul Dubois}
	\title{Mathematics Refresher Course\\First Two Sessions}
	\date{September 2023}
	
	\maketitle
	
	\begin{abstract}
		This course teaches basic mathematical methodologies for proofs.
		It is intended for students with a lack of mathematical background, or with a lack of confidence in mathematics.
		We will try to cover most of the prerequisites of the courses in the master's, i.e. basic algebra/analysis and basic applications.
	\end{abstract}
	
	\section{Presentation}\label{presentation}}
	
	\begin{itemize}
	\tightlist
	\item
	Paul Dubois
	\item
	3rd year PhD @ Centrale / TheraPanacea
	\item
	Research topic: AI applied to radiotherapy
	\item
	Email:
	\href{mailto:b00795695@essec.edu}{\nolinkurl{b00795695@essec.edu}}
	(for any question)
	\item
	Course structure
	
	\begin{itemize}
		\tightlist
		\item
		8*3h arranged as 1h20min lecture - 1/3h break - 1h20min lecture
		\item
		No pb class planned, but lectures will have integrated live
		exercises
		\item
		Interrupt if needed (do \emph{not} wait for the end of the lecture)
	\end{itemize}
	\item
	Examination
	
	\begin{itemize}
		\tightlist
		\item
		The course is pass/fail
		\item
		Spoiler: All of you will pass
		\item
		Home exercises, you will need 80+\% to pass
		\item
		How long do you need to complete exercises (should take 30min to
		1h)?
		\item
		How many exercises do you want? (2-4?)
		\item
		Hand in paper of PDF? (vote)
		\item
		In the unlikely event of not passing, you will be able to do some
		extra work to pass
	\end{itemize}
	\item
	Course notes are still under construction (as I will adjust according
	to the speed of the class); I will give it to you at the end of the
	course.
	\item
	Final questions before we start?
	\end{itemize}
	
	
	
\end{document}