\documentclass[]{article}

%opening
\title{Exercises Set 4}
\author{Paul Dubois}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{stmaryrd}

\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Primes}{\mathbb{P}}
\newcommand{\st}{\text{ s.t. }}
\newcommand{\txtand}{\text{ and }}
\newcommand{\txtor}{\text{ or }}
\newcommand{\lxor}{\veebar}


\begin{document}

	\maketitle
	
	\begin{abstract}
		Only the questions with a * are compulsory (but do all of them!).
	\end{abstract}	
	
	\section{First Order Differential Equations}
	\paragraph{Basics}\mbox{}
	
	\textbf{Exercise 0:}
	Solve the following first-order differential equation:
	\[
	\frac{dy}{dx} = 3x^2 - 2x + 1
	\]
	\textit{Hint:} Integrate both sides with respect to \(x\) to find the solution.
	
	\textbf{Exercise 1:}
	Solve the following first-order differential equation:
	\[
	\frac{dy}{dx} = 5y
	\]
	\textit{Hint:} Calculate the derivative of $\alpha e^{\lambda x}$ and adjust $\alpha$ and $\beta$.
	
	
	\paragraph{Separable}\mbox{}
	
	\textbf{Exercise 2:}
	Solve the following separable differential equation:
	\[
	\frac{dy}{dx} = \frac{x}{y}
	\]
	\textit{Hint:} Separate the variables \(x\) and \(y\), and then integrate both sides to find the solution.
	
	\textbf{Exercise 3:}
	Find the solution to the separable differential equation:
	\[
	\frac{dy}{dx} = 2x^2 e^y
	\]
	\textit{Hint:} Separate the variables \(x\) and \(y\), and then integrate both sides to determine the solution.
	
	\paragraph{Integrating Factor}\mbox{}
	
	\textbf{Exercise 4:}
	Solve the following linear first-order differential equation:
	\[
	\frac{dy}{dx} + 2y = 4x
	\]
	\textit{Hint:} Use an integrating factor.
	
	\textbf{Exercise 5: (*)}
	Find the solution to the linear first-order differential equation:
	\[
	\frac{dy}{dx} - \frac{1}{x}y = x^3
	\]
	\textit{Hint:} Use an integrating factor.
	
	
	
	\section{Second Order Differential Equations}
	\paragraph{Basics}\mbox{}
	
	\textbf{Exercise 0:}
	Solve the following first-order differential equation:
	\[
	\frac{d^2y}{dx^2} = e^x + 4\sin(2x) - 5x
	\]
	\textit{Hint:} Integrate twice both sides with respect to \(x\) to find the solution.
	
	\textbf{Exercise 1:}
	Find the general solution to the differential equation:
	\[
	\frac{d^2y}{dx^2} + 2\frac{dy}{dx} + y = 0
	\]
	\textit{Hint:} Assume a solution of the form \(y(x) = e^{rx}\) and find the values of \(r\) that satisfy the equation.
	
	\textbf{Exercise 2:}
	Find the general solution to the differential equation:
	\[
	\frac{d^2y}{dx^2} + 4y = 0
	\]
	\textit{Hint:} Assume a solution of the form \(y(x) = e^{rx}\) and find the values of \(r\) that satisfy the equation ($r$ may be complex... what is exponential of a complex number?).
	
	\paragraph{Separable}\mbox{}
	
	\textbf{Exercise 3:}
	Solve the following separable differential equation:
	$$y'' = (y')^2$$
	\textit{Hint:} Separate the variables.
	
	\paragraph{Non-homogeneous}\mbox{}
	
	\textbf{Exercise 4:}
	Consider the non-homogeneous linear second-order differential equation with constant coefficients:
	\[
	\frac{d^2y}{dx^2} + 4\frac{dy}{dx} + 4y = 6x^2 + 10x + 2
	\]
	\textit{Hint:} Begin by finding the general solution to the associated homogeneous equation. Then, use the method of undetermined coefficients to find a particular solution for the non-homogeneous part.
	
	\textbf{Exercise 5:}
	Solve the following non-homogeneous linear second-order differential equation with constant coefficients:
	\[
	\frac{d^2y}{dt^2} - 2\frac{dy}{dt} + 5y = 3e^{2t}
	\]
	\textit{Hint:} First, find the general solution to the homogeneous equation. Then, use the method of undetermined coefficients to find a particular solution for the non-homogeneous part.
	
	\paragraph{Boundary Conditions}\mbox{}
	
	\textbf{Exercise 6:}
	Consider the differential equation:
	\[
	\frac{d^2y}{dx^2} + 2\frac{dy}{dx} - 3y = 0
	\]
	Find the particular solution of this differential equation that satisfies the boundary conditions \(y(0) = 1\) and \(y(2) = 5\).
	\textit{Hint:} First, solve the homogeneous equation, and then find a particular solution that satisfies the given boundary conditions.
	
	\textbf{Exercise 7: (*)}
	Given the differential equation:
	\[
	\frac{d^2y}{dx^2} + 4y = 12x
	\]
	Find the particular solution of this differential equation subject to the boundary conditions \(y(0) = 0\) and \(y'(0) = 2\).
	\textit{Hint:} Solve the homogeneous equation, find a particular solution for the non-homogeneous part, and apply the given boundary conditions.
	
	
	

\end{document}
